---
title: "Course Schedule Survey - Groups"
subtitle: "Student Sample (n = 288) "
author: "James Van Slyke"
date: today
format: 
  html:
    toc: true
    toc-location: left
    toc-expand: true
    toc-depth: 3
editor: visual
---

```{r}
#| echo: false
#| include: false
#| message: false
library(tidyverse)
library(gt)
library(readr)
CS_Student <- read_csv("/Users/jamesvanslyke/Library/CloudStorage/GoogleDrive-james.vanslyke@gmail.com/My Drive/Current/FPU/Admin/FPU Admin Projects/Course Schedule Surveys/Data/CS_Student.csv")

#Dataset Cleaning
#Remove unwanted rows 
CS_Student <- CS_Student %>% 
  slice(-c(1, 2))

#Select the columns that you want 
CS_Student <- CS_Student |> 
  select(Q16:Q12)

#Remove NAs
# Remove rows where column 'A' has NA
CS_Student <- CS_Student |>  
  filter(!is.na(Q16))

```

## Athletes vs. Non-athletes

### Hybrid courses are courses in which you meet in-person and online, usually alternating days. Given the opportunity, would you be interested in taking hybrid courses?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  mutate(Q7 = case_when(
    Q7 == "Yes" ~ "Athlete",
    Q7 == "No" ~ "Non-Athlete")) |> 
  group_by(Q7) |> 
  count(Q10) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q10, y = Percentage, fill = Q7)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
    scale_x_discrete(limits = c("Definitely not", "Probably not", "Might or might not", "Probably yes", "Definitely yes" )) +
  labs(x ="", fill = "Student Sample")
```

### For online classes, do you prefer that they have a zoom component or that it's completely asynchronous?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  mutate(Q7 = case_when(
    Q7 == "Yes" ~ "Athlete",
    Q7 == "No" ~ "Non-Athlete")) |> 
  group_by(Q7) |> 
  count(Q15) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q15, y = Percentage, fill = Q7)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
  labs(x ="", fill = "Student Sample")
```

### Rank your preferences from 0 to 10 for the following types of courses

```{r}
#| echo: false
#| message: false
#| warning: false
CS_Student |> 
  select(Q7, Q19_1:Q19_3) |> 
  drop_na() |> 
  rename(Athlete = Q7, 
         Hybrid = Q19_1,
         Online = Q19_2,
         In_person = Q19_3) |> 
  mutate(Athlete = case_when(
    Athlete == "Yes" ~ "Athlete",
    Athlete == "No" ~ "Non-Athlete")) |> 
  pivot_longer(cols = c(Hybrid, Online, In_person), 
               names_to = "Class", 
               values_to = "Preference") |> 
  mutate(Preference = as.numeric(Preference)) |> 
  group_by(Athlete, Class) |> 
  summarize(n = n(),
            mean = mean(Preference),
            sd = sd(Preference),
            se = sd / sqrt(n),
            ci = qt(0.975, df = n - 1) * sd / sqrt(n)) |> 
  ggplot( aes(x = Class,
              y = mean, fill = Athlete)) +
  theme_minimal() +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  geom_errorbar(aes(ymin=mean-ci,
                    ymax=mean+ci), 
                position = position_dodge(0.7), width = 0.2) +
  labs(y = "Mean Preference", x = "Type of Class") +
  scale_x_discrete(limits = c("In_person", "Online", "Hybrid"))
```

## Commuting vs. On campus Students

### Hybrid courses are courses in which you meet in-person and online, usually alternating days. Given the opportunity, would you be interested in taking hybrid courses?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  group_by(Q2) |> 
  count(Q10) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q10, y = Percentage, fill = Q2)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
  scale_x_discrete(limits = c("Definitely not", "Probably not", "Might or might not", "Probably yes", "Definitely yes" )) +
  labs(x ="", fill = "Type of Student")
```

### For online classes, do you prefer that they have a zoom component or that it's completely asynchronous?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  group_by(Q2) |> 
  count(Q15) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q15, y = Percentage, fill = Q2)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
  labs(x ="", fill = "Type of Student")
```

### Rank your preferences from 0 to 10 for the following types of courses

```{r}
#| echo: false
#| warning: false
#| message: false
CS_Student |> 
  select(Q2, Q19_1:Q19_3) |> 
  drop_na() |> 
  rename(Hybrid = Q19_1,
         Online = Q19_2,
         In_person = Q19_3) |> 
  pivot_longer(cols = c(Hybrid, Online, In_person), 
               names_to = "Class", 
               values_to = "Preference") |> 
  mutate(Preference = as.numeric(Preference)) |>
  group_by(Q2, Class) |> 
  summarize(n = n(),
            mean = mean(Preference),
            sd = sd(Preference),
            se = sd / sqrt(n),
            ci = qt(0.975, df = n - 1) * sd / sqrt(n)) |> 
  ggplot( aes(x = Class,
              y = mean, fill = Q2)) +
  theme_minimal() +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  geom_errorbar(aes(ymin=mean-ci,
                    ymax=mean+ci), 
                position = position_dodge(0.7), width = 0.2) +
  labs(y = "Mean Preference", x = "Type of Class", fill = "Type of Student") +
  scale_x_discrete(limits = c("In_person", "Online", "Hybrid"))
```

## On campus vs. Off campus jobs

### Hybrid courses are courses in which you meet in-person and online, usually alternating days. Given the opportunity, would you be interested in taking hybrid courses?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  group_by(Q13) |> 
  count(Q10) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q10, y = Percentage, fill = Q13)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
    scale_x_discrete(limits = c("Definitely not", "Probably not", "Might or might not", "Probably yes", "Definitely yes" )) +
  labs(x ="", fill = "Student Job")
```

### For online classes, do you prefer that they have a zoom component or that it's completely asynchronous?

```{r}
#| echo: false 
#| message: false
#| warning: false
CS_Student |> 
  group_by(Q13) |> 
  count(Q15) |> 
  drop_na() |> 
  mutate(Percentage = n /sum(n)*100) |> 
  ggplot( aes(x = Q15, y = Percentage, fill = Q13)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  theme_minimal() + 
  labs(x ="", fill = "Student Job")
```

### Rank your preferences from 0 to 10 for the following types of courses

```{r}
#| echo: false
#| message: false
#| warning: false
CS_Student |> 
  select(Q13, Q19_1:Q19_3) |> 
  drop_na() |> 
  rename(Hybrid = Q19_1,
         Online = Q19_2,
         In_person = Q19_3) |> 
  pivot_longer(cols = c(Hybrid, Online, In_person), 
               names_to = "Class", 
               values_to = "Preference") |> 
  mutate(Preference = as.numeric(Preference)) |>
  group_by(Q13, Class) |> 
  summarize(n = n(),
            mean = mean(Preference),
            sd = sd(Preference),
            se = sd / sqrt(n),
            ci = qt(0.975, df = n - 1) * sd / sqrt(n)) |> 
  ggplot( aes(x = Class,
              y = mean, fill = Q13)) +
  theme_minimal() +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  geom_errorbar(aes(ymin=mean-ci,
                    ymax=mean+ci), 
                position = position_dodge(0.7), width = 0.2) +
  labs(y = "Mean Preference", x = "Type of Class", fill = "Student Job") +
  scale_x_discrete(limits = c("In_person", "Online", "Hybrid"))
```
